\section{Project Plan}
\subsection{Risks and Risk Management Strategies}
The risks for the project can be found on Appendix A. The biggest risk for the project will most likey be getting the community involved by using our application as the data that we will be showing depends on them.
\subsection{Timeline}
The project will run from April 2019 till 31 November 2019. The full timeline for the project is shown in Appendix B as a form of the Gantt Chart and a Milestone table.
\subsection{Required Resources}
The resources required are as follows:
\begin{itemize}
	\item IDE for developing this application. For this we are going to use Android Studio \cite{android_developers}.
	\item  We will need a database system to store the data that we record. For this we have selected a time series database.
	\item We will need a server that will host the database.
	\item A server for the application is also needed.
	\item We will need users for testing the application.
\end{itemize}
\subsection{Deliverables}
The main deliverables for the application will be a QoS Monitoring system. This will comprise of a mobile application that is capable of collection network measurements from the end users and the firewalls. We will also have an Orchestration tool that will be useful to network administrators and researchers for scheduling and triggering network data collections from devices. Finally, we will have a visualizer tool for users to be able to have a visual idea of the network activity. The other deliverables are as follows:
\begin{itemize}
	\item The Literature Review
	\item The Project Proposal
	\item Presentation of the Proposal
	\item Prototypes of the Systems
	\item Project Website
	\item A final Report
\end{itemize}
\subsection{Milestones}
The milestone for the project can be viewed in Appendix B together with the Gantt Chart. Milestones will include the project deliverables.
\subsection{Work Allocation}
The work is divided between the three people involved, Clayton Sibanda, David Kheri and Meluleki Dube. The division is as follows:
\begin{itemize}
	\item Clayton Sibanda is working on the visualizer tool for the application. This will involve coming up with the website where users will be able to visit to see the network activity and their network activity profiles.
	\item David Kheri is working on the Orchestration tool that will help researchers and network administrators to trigger and schedule data collection from the end users. David will explore using this tool to confirm potential network threats.
	\item  Meluleki Dube is working on creating the application for collecting network data and saving the measured data on a database that will be queried by different users for different reasons. This database will be queried by the visualizer that Clayton is working on and by David on when collecting the network results collected from the devices.
\end{itemize}
